Fig2: Candidate genes

### 2020-07-31 analysis/figure-2.Rmd
better new fig 2

```{r newHPGfig}

a <- candidateboxplot("gonad", c("COMT"), "female") + 
  labs(title =  "Females", 
       subtitle = "Hypothlamic expression" )

b <- externalboxplots("gonad", c("COMT"), "female") + 
  labs(title =  "Females", 
       subtitle = "Hypothlamic expression" )

c <- candidateboxplot("pituitary", c("PRL"), "female") + 
  labs(subtitle = "Pituitary expression" )

d <- externalboxplots("pituitary", c("PRL"), "female") + 
   labs(subtitle = "Pituitary expression" )

e <- candidateboxplot("gonad", c("AVPR1A"), "female") + 
  labs( subtitle = "Gonad expression" ) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

f <- externalboxplots("pituitary", c("AVPR1A"), "female") + 
   labs( subtitle = "Gonad expression" ) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

a2 <- candidateboxplot("gonad", c("COMT"), "male") + 
  labs(title =  "Males", 
       subtitle = "Hypothlamic expression" )

b2 <- externalboxplots("gonad", c("COMT"), "male") + 
  labs(title =  "Males", 
       subtitle = "Hypothlamic expression" )

c2 <- candidateboxplot("pituitary", c("PRL"), "male") + 
  labs(subtitle = "Pituitary expression" )

d2 <- externalboxplots("pituitary", c("PRL"), "male") + 
   labs(subtitle = "Pituitary expression" )

e2 <- candidateboxplot("gonad", c("AVPR1A"), "male") + 
  labs( subtitle = "Gonad expression" ) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

f2 <- externalboxplots("pituitary", c("AVPR1A"), "male") + 
   labs( subtitle = "Gonad expression" )  + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

newfig2 <- plot_grid(females, males)
newfig2
```

>>>>

a <- candidateboxplot("hypothalamus", c("COMT"), "female") + 
  labs(title =  "Sequential", 
       subtitle = "Female hypothalamus" )

b <- externalboxplots("hypothalamus", c("COMT"), "female") + 
  labs(title =  "External", 
       subtitle = " " )

c <- candidateboxplot("pituitary", c("PRL"), "female") + 
  labs(subtitle = "Female pituitary" )

d <- externalboxplots("pituitary", c("PRL"), "female") + 
   labs(subtitle = " " )

e <- candidateboxplot("gonad", c("AVPR1A"), "female") + 
  labs( subtitle = "Female gonads" ) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

f <- externalboxplots("pituitary", c("AVPR1A"), "female") + 
   labs( subtitle = " " ) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

a2 <- candidateboxplot("hypothalamus", c("COMT"), "male") + 
  labs(title =  "Sequential", 
       subtitle = "Male hypothalamus" )

b2 <- externalboxplots("hypothalamus", c("COMT"), "male") + 
  labs(title =  "External", 
       subtitle = "  " )

c2 <- candidateboxplot("pituitary", c("PRL"), "male") + 
  labs(subtitle = "Male pituitary" )

d2 <- externalboxplots("pituitary", c("PRL"), "male") + 
   labs(subtitle = " " )

e2 <- candidateboxplot("gonad", c("AVPR1A"), "male") + 
  labs( subtitle = "Male gonads" ) + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

f2 <- externalboxplots("pituitary", c("AVPR1A"), "male") + 
   labs( subtitle = " " )  + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

@@

newfig2 <- plot_grid(females, males, labels = c("A", "B"),
                     label_size  = 8)
newfig2
```
